Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2020-12-21 manuscript/draft_rsfmri.Rmd

Further, we evaluated the impact of our denoising pipelines. Table \@ref(tab:tableQcfc) shows that in the minimally preprocessed data, mFD and connectivity was significantly positively correlated (mean Spearman's r = `r round(res[1,1],2)`), with a strong distance dependence (mean Spearman's r = `r round(res[1,5],2)`).  Denoising procedures (AROMA, AROMA+CC, AROMA+CC+GSR) gradually reduced the correlation of mFD and connectivity, and also alleviated the distance dependency. AROMA+CC+GSR performed best, with almost no mFD-FC correlation (mean Spearman's r = `r round(res[4,1],2)`), and minimal positive distance dependence (mean Spearman's r = `r round(res[4,5],2)`). Yet, AROMA+CC also performed well, and we thus calculated our analysis models for both preprocessing schemes.
Figure \@ref{fig:figNetworks} shows the DMN and reward network which we used for extracting the aggregated FC valued. Both networks include previously described brain regions (i.e. medial prefrontal cortex, parietal lobules and posterior hippocampus for the DMN, and anterior cingulare, right amygdala and ventromedial-prefrontal cortex for the reward network). Yet, the reward network is less pronounced (overall lower T-values) and symmetric (no significant connectivity with left amygdala), which might be due to SNR differences in the seed brain regions (see Figure \@{ref:fig:figtSNR}.
>>>>>>> include glass brain of networks and LLMMs into draft

@@

## Interaction effect of intervention and time (preregistered analysis)
### DMN/reward network with whole brain mask (preregistered analysis)

>>>>

Further, we evaluated the impact of our denoising pipelines. Table \@ref(tab:tableQcfc) shows that in the minimally preprocessed data, mFD and connectivity was significantly positively correlated (mean Spearman's r = `r round(res[1,1],2)`), with a strong distance dependence (mean Spearman's r = `r round(res[1,5],2)`).  Denoising procedures (AROMA, AROMA+CC, AROMA+CC+GSR) gradually reduced the correlation of mFD and connectivity, and also alleviated the distance dependency. AROMA+CC+GSR performed best, with almost no mFD-FC correlation (mean Spearman's r = `r round(res[4,1],2)`), and minimal positive distance dependence (mean Spearman's r = `r round(res[4,5],2)`). Yet, AROMA+CC also performed well, and we thus calculated our analysis models for both preprocessing schemes.
Figure \@ref{fig:figNetworks} shows the DMN and reward network which we used for extracting the aggregated FC valued. Both networks include previously described brain regions (i.e. medial prefrontal cortex, parietal lobules and posterior hippocampus for the DMN, and anterior cingulare, right amygdala and ventromedial-prefrontal cortex for the reward network). Yet, the reward network is less pronounced (overall lower T-values) and symmetric (no significant connectivity with left amygdala), which might be due to SNR differences in the seed brain regions (see Figure \@{ref:fig:figtSNR}.

@@

=======

>>>>>>> 30e451a04dedc0054f54c9f8b5bb0ffb11922e68
## Interaction effect of intervention and time (preregistered analysis)
### DMN/reward network with whole brain mask (preregistered analysis)
